---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# dataanalysis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Travis build status](https://travis-ci.com/srmatth/dataanalysis.svg?branch=main)](https://travis-ci.com/srmatth/dataanalysis)
[![Codecov test coverage](https://codecov.io/gh/srmatth/dataanalysis/branch/main/graph/badge.svg)](https://codecov.io/gh/srmatth/dataanalysis?branch=main)
<!-- badges: end -->

A package containing functions that will aid in performing a data analysis, and especially in writing up the report.

## Installation

You can download this package from Github using the following code:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("srmatth/dataanalysis")
```

## Basic Usage

## Acknowledgements 

A large portion of this code was adapted from [Professor Dan Gillen](https://dgillen.ics.uci.edu/).

## Code of Conduct

Please note that the dataanalysis project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
